Detection of an Intrinsic Color Parameter within the Type~Ia Supernovae of the Nearby Supernova Factory

### 2016-09-23 forgerard.tex
logging on ahead

>>>>

\section{Interpreting $k$ and $D$ As Parameters of a Single Dust Model}
%ipdb> print y, y-ymin, ymax-y
%2.23720862938 0.00612061774367 0.00623996846008
%ipdb> (y,ymin,ymax)  = numpy.percentile(samples[:,1],(50,50-34,50+34)) 
%ipdb> print y, y-ymin, ymax-y
%-3.46707773157e-05 0.000555359008477 0.000616592111953
Until now we have considered $k$ and $D$ as independent external and internal parameters.  However, they may be both
parameters of a single underlying dust.  Indeed the CCM dust law can be exactly written as a two-parameter linear model
\begin{equation}
A_X = A_V a(X) + E(B-V) b(X).
\end{equation}
The Fitzpatrick model can also approximately be described by a linear model in the range of $R_V$ and wavelength under consideration:
the results shown here vary only at the percent level when making this approximation.

In our model, variations in $k$ and $D$ affect magnitudes in two directions in magnitude space
$\frac{\partial A}{\partial E_\delta(B-V)}$, $\frac{\partial A}{\partial E_\gamma(B-V)}$.  In the Fitzpatrick model
variations on $E^F(B-V)$ and $A^F_V=R^F_VE^F(B-V)$ induce magnitude changes in
in directions
$\frac{\partial A}{\partial E^F(B-V)}$, $\frac{\partial A}{\partial A^F_V}$.
The planes in magnitude-space defined by each pair of vectors are nearly parallel, in that
\begin{equation}
\begin{pmatrix}
\frac{\partial A}{\partial E_\delta(B-V)} \\
\frac{\partial A}{\partial E_\gamma(B-V)}
\end{pmatrix}=
\begin{pmatrix}
0.74 & -5.45 \\
1.15 & 2.84
\end{pmatrix} 
\begin{pmatrix}
\frac{\partial A}{\partial R^F_V} \\
\frac{\partial A}{\partial A^F_V}
\end{pmatrix}+
\vec{\epsilon},
\end{equation}
where the residual $\vec{\epsilon}$''s perpendicular to the Fitzpatrick plane
contribute  5\% and 2\% to the total  length of the vector.

The projections of our model parameters $E_\delta(B-V)$ and  $E_\gamma(B-V)$ for the supernovae in our sample
onto the Fitzpatrick plane
have corresponding values of $E^F(B-V)$ and $A^F$, up to a constant.  These are shown in Figure~\ref{avebv:fig}.
The points are confined to a tight locus around a line, with slope that corresponds to $R^F_V=2.5$.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5in]{output11/avebv_synth.pdf}
    \caption{\textcolor{red}{Projections of our model parameters $E_\delta(B-V)$ and  $E_\gamma(B-V)$ for the supernovae in our sample
onto the Fitzpatrick plane.}
   \label{avebv:fig}}
\end{figure}

The linear fit produces the zeropoint (which happens to be consistent with zero) along with the slope, allowing us to determine $R^F_V$ for each supernova,
as shown in Figure~\ref{avrv:fig}.  An interesting feature is that the distribution at extreme blue colors seems to be different from the distribution for redder objects.
I will contemplate whether this could mean anything.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5in]{output11/avrv_synth.pdf}
    \caption{\textcolor{red}{$R^F_V$ for each supernova.}
   \label{avrv:fig}}
\end{figure}

The near coplanarity of the plane defined by our parameters and the plane of Fitzpatrick, together with the fact that our the individual supernova
parameters translate to Fitzpatrick parameters consistent with a distribution expected for a narrow range of $R^F_V$ lead us to conclude that 
external dust is responsible for most of our $k$ and $D$ parameters.
